---
knit: "bookdown::render_book"
title: Notes on British ants
author: Graham French
date: '`r Sys.Date()`'
output: 
  bookdown::tufte_handout2:
    includes:
      in_header: format.tex
    toc: true
    toc_depth: 1
    highlight: tango
    keep_tex: true
fontsize: 10pt
bibliography: ["ants.bib", "r.bib"]
csl: biological-reviews-modified.csl
nocite: | 
  @R-base, @R-bookdown, @R-knitr, @R-markdown, @R-tufte
site: bookdown::bookdown_site
documentclass: book
---
\pagebreak

```{r markdown, echo = FALSE, purl = FALSE, warning = FALSE}
library(knitr)
library(bookdown)
library(tufte)
opts_chunk$set(echo = TRUE, eval = FALSE, warning = FALSE, error = FALSE, comment = NA, cache = FALSE)
# write_bib(c("knitr", "bookdown", "markdown", "tufte"))
```

```{r packagesBibliography, echo = FALSE, eval = FALSE, purl = FALSE,}
write_bib(c("knitr", "bookdown", "markdown", "tufte"))
```

# **Introduction** {-}

These notes on the British species of ants were made whilst reading a number of books [@Donisthorpe; @Czechowski; @Pontin; @Skinner-1987; @Skinner-1996], pdf files [@Macdonald] and online resources [@Antweb; @AntWiki; @BWARS].

The distribution maps were created from records collated by the Bees, Wasps and Ants Recording Society and made publically available through the NBN Gateway in March 2014 [@BWARSdata; @NBNGateway].

\pagebreak

